A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-03-16 graph_syntax.tex
a little more re-org, again...

\section{New Graph--based Syntax}
The ultimate goal of the new graph--based syntax presented here is to be able to 
fully describe the fundamental problem formulation for a complex design task, 
while still being able to accomodate the more specific case when a solution 
strategy is applied to the problem formulation. In order to achieve that goal 
the graph needs to accomodate a number of constructs from MDAO problems:

\begin{itemize}
    \item Analysis tools and connections between them
    \item Coupling between analyses
    \item Design Variable
    \item Objectives and constraints
    \item Local and global properties
\end{itemize}

@@

\subsection{MDAO Graph Primatives}
There are three node types:  
\begin{description}
\item[variable node] represents passing of data.
\item[model node] represents the handling of data.
\item[driver node] represents constrol structures capable of managing iteration
\end{description}

@@

\subsubsection{Analysis Blocks and Connections}

@@

\subsubsection{Design Variables, Objectives, and Constraints}

\subsubsection{Local vs Global}

\subsubsection{}

@@

\section{Graph--based Representation of the Fundamental Problem Formulation}

In this section we introduce the remaining necessary notion and give graph--theory based definitions of the MCG and FPF, and then process to demonstrate how the FPF is obtained from the MCG.

\subsection{Additional Notation}
For node $v \in V$ the edges directed out are given by $E(v)$ and the edges directed into $v$ are given by $E^{-1}(v)$; $E(E(v))$ is denoted as $E^2(v)$, and likewise for additional levels. 
The \emph{indegree} of a node is the number of edges directed in and is denoted as $\txt{deg}^-(v)$, and the \emph{outdegree} is the number of edges directed out and it is denoted as $\txt{deg}^+(v)$.
We also define the \emph{upper indegree limit} 
\begin{equation}
\txt{deg}_u^-(v):V \to \mathbb{N}
\end{equation} 
and the \emph{lower indegree limit}
\begin{equation}
\txt{deg}_l^-(v):V \to \mathbb{N}.
\end{equation}
These user-specified limits set the number of edges that may be directed into a node for a problem formulation to be valid. For example, a variable node $v$ will have $\txt{deg}_u^-(v) = \txt{deg}_l^-(v) = 1$, unless it is a multi--fidelity variable, in which case the user may specify some upper limit higher than one.

@@

>>>>

\section{Requirements for New Graph Syntax}
The ultimate goal of the new graph--based syntax presented here is to be able to 
fully describe the fundamental problem formulation for a complex design task, 
while still being able to accomodate the more specific case when a solution 
strategy is applied to the problem formulation. In order to achieve that goal 
the graph needs to accomodate a number of constructs from MDAO problems:

\begin{itemize}
    \item Analysis tools and connections between them
    \item Design variables, objectives, and constraints
    \item Local and global properties
    \item Coupling between analyses
    \item Multi-fidelity analyses
\end{itemize}

@@

\section{MDAO Graph Primatives}
There are three node types:  
\begin{description}
\item[variable node] represents passing of data.
\item[model node] represents the handling of data.
\item[driver node] represents constrol structures capable of managing iteration
\end{description}

@@

\subsection{Analysis Blocks and Connections}

@@

\subsection{Design Variables, Objectives, and Constraints}

@@

\subsection{Local vs Global Properties}

\subsection{Coupling Between Analyses}

\subsection{Multi-fidelity Analyses}

For node $v \in V$ the edges directed out are given by $E(v)$ and the edges directed into $v$ are given by $E^{-1}(v)$; $E(E(v))$ is denoted as $E^2(v)$, and likewise for additional levels. 
The \emph{indegree} of a node is the number of edges directed in and is denoted as $\txt{deg}^-(v)$, and the \emph{outdegree} is the number of edges directed out and it is denoted as $\txt{deg}^+(v)$.
We also define the \emph{upper indegree limit} 
\begin{equation}
\txt{deg}_u^-(v):V \to \mathbb{N}
\end{equation} 
and the \emph{lower indegree limit}
\begin{equation}
\txt{deg}_l^-(v):V \to \mathbb{N}.
\end{equation}
These user-specified limits set the number of edges that may be directed into a node for a problem formulation to be valid. For example, a variable node $v$ will have $\txt{deg}_u^-(v) = \txt{deg}_l^-(v) = 1$, unless it is a multi--fidelity variable, in which case the user may specify some upper limit higher than one.

@@

\section{Building MCG, FPF, and SPF Graphs}
